% !TeX root = ../main.tex

\ustcsetup{
	keywords = {
		二维隐马尔科夫模型, Kaldi开源工具库, 手写孤立汉字识别
	},
	keywords* = {
		Handwritten Chinese character recognition, Two-Dimensional Hidden Markov Model, Kaldi open source toolkit
	},
}

\begin{abstract}
	
	
	
	本篇论文从解决汉字空间结构的精细分割这一问题出发，
	提出并实现了一套完整的二维隐马尔科夫模型解决方案。
	
	此次提出的解决方案有以下两个优点：
	
	第一，相较于往常的一维隐马尔科夫模型，二维隐马尔科夫模型更加适合于捕捉汉字之间复杂的空间结构，其自由的状态转移
	方式也使得不同隐状态可以描述汉字中任意不规则的区域，这种二维帧级建模的灵活性是在一维隐马尔科夫模型中无法实现的。
	
	第二，本次解决方案提供了集成到kaldi工具库内部的源码，以及完整的特征提取、模型训练、解码的脚本程序，并且带有详细的
	使用说明，相信这份开源工具可以在汉字识别之外的其他相似领域也能发挥一定的作用。
	
	经过在中科院自动化所发布的HDWB-1.0、HWDB-1.1数据库中的50类汉字实验，初步证明了二维隐马尔科夫模型在汉字建模不论是在
	识别准确率还是建模精细度上，相较于一维隐马尔科夫模型都有着较为明显的优势。
	
\end{abstract}

\begin{enabstract}
	Starting from solving the problem of fine segmentation of the spatial structure of Chinese characters, 
	this paper proposes and implements a complete set of two-dimensional hidden Markov model solutions.
	
	The solution proposed has the following two advantages:
	
	First, compared with the usual one-dimensional hidden Markov model, 
	the two-dimensional hidden Markov model is more suitable for capturing the complex spatial structure between Chinese characters, 
	and its free state transitions also allows different hidden states to describe any irregular region of Chinese characters. 
	The flexibility of this two-dimensional frame-level modeling cannot be realized in the one-dimensional hidden Markov model.
	
	Second, this solution provides the source code integrated into the Kaldi tool library, 
	as well as a complete feature extraction, model training, and decoding script program,
	with detailed instructions for use. Other similar fields outside can also play a role.
	
	After the experiment of 50 types of Chinese characters in the HDWB-1.0 
	and HWDB-1.1 databases released by the Chinese Academy of Sciences Automation, 
	it is initially proved that the two-dimensional hidden Markov model in Chinese 
	character modeling is not only in recognition accuracy or modeling precision, 
	Compared with the one-dimensional hidden Markov model, it has obvious advantages.
	
\end{enabstract}
